---
title: "Metagenomic Biosurveillance Network"
output:
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bootswatch: minty # We can set color themes!
      #Also check out help on bs_themer
    vertical_layout: fill
    orientation: rows
    source_code: embed
# If we Output HTML, this allows Latex for the Documentation:  
# mathjax: "http://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
runtime: shiny
---


```{r setup, include=FALSE}
library(tidyverse)
library(shiny)
library(flexdashboard)

source("Stochastic.R", local = TRUE)
load("results.RData")

# Define disease parameter names and their descriptions
disease_params <- c(
  "beta" = "Transmission rate (contacts per day)",
  "sigma" = "Progression rate (1/days in E)",
  "gamma" = "Recovery rate (1/days in I)",
  "delta" = "Proportion of infections requiring hospital care",
  "theta" = "Rate of hospital presentation (1/days until seeking care)"
)
```



Sidebar {.sidebar}
=====================================

### Model Inputs

```{r}
# Add "Custom" option to the disease scenarios
choices <- c(row.names(all_params), "Custom")

selectInput(
  inputId = "Disease_Scenario",
  label = "Disease Scenario",
  choices = choices,
  selected = 1,
  multiple = FALSE
)

# UI for custom parameters - initially hidden
conditionalPanel(
  condition = "input.Disease_Scenario == 'Custom'",
  h4("Custom Disease Parameters"),
  
  numericInput(
    inputId = "beta_custom",
    label = disease_params["beta"],
    value = 0.3,
    min = 0.01,
    max = 2,
    step = 0.01
  ),
  
  numericInput(
    inputId = "sigma_custom",
    label = disease_params["sigma"],
    value = 0.2,
    min = 0.01,
    max = 1,
    step = 0.01
  ),
  
  numericInput(
    inputId = "gamma_custom",
    label = disease_params["gamma"],
    value = 0.1,
    min = 0.01,
    max = 1,
    step = 0.01
  ),
  
  numericInput(
    inputId = "delta_custom",
    label = disease_params["delta"],
    value = 0.05,
    min = 0.001,
    max = 0.5,
    step = 0.001
  ),
  
  numericInput(
    inputId = "theta_custom",
    label = disease_params["theta"],
    value = 0.5,
    min = 0.01,
    max = 1,
    step = 0.01
  )
)

sliderInput(
  inputId = "Threshold",
  label = "Detections needed to confirm disease",
  min = 1,
  max = 5,
  value = 1,
  step = 2,
  ticks = FALSE
)
```

### Simulations

```{r}
div(style = "display: flex;",
  actionButton("select_top_n", "Select K largest hospitals", style = "margin-right: 5px;"),
  div(style = "width: 70px;", numericInput("top_n", label = NULL, value = 1,
            min = 1, max = length(Hospital_visitors$Hospital)))
)
selectizeInput(
  inputId = "selected_hospitals",
  label = "Hospitals participating in MBN",
  choices = Hospital_visitors$Hospital,
  selected = Hospital_visitors$Hospital[1:6],
  multiple = TRUE,
  options = list(placeholder = "Select hospitals...")
)
div(style = "display: flex;",
  actionButton("run", "Run N simulations", style = "margin-right: 5px;"),
  div(style = "width: 70px;", numericInput("rep", label = NULL, value = 10, min = 1,))
)
```

### Costs

```{r}
selectInput(
  inputId = "y_axis",
  label = "Y-axis of costs plot",
  choices = c(
    "Infections in population until detection" = "cases",
    "ED presentations until detection" = "hosp",
    "Time (days) until detection" = "time"
    ),
  multiple = FALSE
)
```

Simulations
=======================================================================

### The blue dot shows the median number of days and number of infections in the total population upon detection by MBN, and error bars show the interquartile range. The grey lines show individual simulation runs.
```{r}
# Modified function to handle custom disease parameters
simulatedData <- eventReactive(input$run, {
  # Check if custom disease was selected
  if (input$Disease_Scenario == "Custom") {
    # Create a custom parameter set
    custom_params <- c(
      beta = input$beta_custom,
      sigma = input$sigma_custom,
      gamma = input$gamma_custom,
      delta = input$delta_custom,
      theta = input$theta_custom,
      tau = 0.77  # Default sensitivity
    )
    
    # Run the custom model
    run_SEIR_custom(
      custom_params = custom_params,
      rep = input$rep,
      threshold = input$Threshold,
      mu = coverage(input$selected_hospitals)
    )
  } else {
    # Run with predefined disease
    run_SEIR(
      disease_name = input$Disease_Scenario,
      rep = input$rep,
      threshold = input$Threshold,
      mu = coverage(input$selected_hospitals)
    )
  }
})

observeEvent(input$select_top_n, {
  # Check if the input is within the available range
  if (input$top_n >= 1 && input$top_n <= length(Hospital_visitors$Hospital)) {
    # Select the top N hospitals
    top_n_hospitals <- head(Hospital_visitors$Hospital, n = input$top_n)
    updateSelectizeInput(session, "selected_hospitals", selected = top_n_hospitals)
  }
})

renderPlot({
  data <- simulatedData()
  plot_SEIR(data)
})
```


Cost-effectiveness
=======================================================================

### The blue line is the median outcome of 1000 pre-run simulations, and the grey area shows the interquartile range. In the sidebar, you can select a metric to show on the y-axis.
```{r}
subset_data <- reactive({
  # For custom disease, don't attempt to show pre-computed cost effectiveness
  if (input$Disease_Scenario == "Custom") {
    # Return empty dataframe or show a message
    return(NULL)
  } else {
    results %>% 
      filter(d == input$Disease_Scenario, t == input$Threshold, output == input$y_axis)
  }
})

renderPlot({
  data <- subset_data()
  if (is.null(data) || nrow(data) == 0) {
    # Create an empty plot with a message for custom disease
    ggplot() + 
      annotate("text", x = 0.5, y = 0.5, 
               label = "Cost-effectiveness plot not available for custom disease parameters.\nRun simulations with pre-defined diseases to view this plot.", 
               size = 6) +
      theme_void() +
      xlim(0, 1) + ylim(0, 1)
  } else {
    plot_cost(data)
  }
})
```


Model Documentation
=======================================================================

Row
-----------------------------------------------------------------------
```{r test, child="Documentation.RMD", eval=TRUE, local=TRUE}
```