---
title: "Metagenomic Biosurveillance Network"
author: "Meusel et al."
output:
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bootswatch: minty # We can set color themes!
      #Also check out help on bs_themer
    vertical_layout: fill
    orientation: rows
    source_code: embed
# If we Output HTML, this allows Latex for the Documentation:  
# mathjax: "http://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
runtime: shiny
---


```{r setup, include=FALSE}
library(tidyverse)
library(shiny)
library(flexdashboard)

source("Stochastic.R", local = TRUE)
load("results.RData")
```



Sidebar {.sidebar}
=====================================

### Model Inputs

```{r}
selectInput(
  inputId = "Disease_Scenario",
  label = "Disease Scenario",
  choices = row.names(all_params),
  selected = 1,
  multiple = FALSE
)
sliderInput(
  inputId = "Threshold",
  label = "Detections needed to confirm disease",
  min = 1,
  max = 5,
  value = 1,
  step = 2,
  ticks = FALSE
)
```

### Simulations

```{r}
div(style = "display: flex;",
  actionButton("select_top_n", "Select K largest hospitals", style = "margin-right: 5px;"),
  div(style = "width: 70px;", numericInput("top_n", label = NULL, value = 1,
            min = 1, max = length(Hospital_visitors$Hospital)))
)
selectizeInput(
  inputId = "selected_hospitals",
  label = "Hospitals participating in MBN",
  choices = Hospital_visitors$Hospital,
  selected = Hospital_visitors$Hospital[1:6],
  multiple = TRUE,
  options = list(placeholder = "Select hospitals...")
)
div(style = "display: flex;",
  actionButton("run", "Run N simulations", style = "margin-right: 5px;"),
  div(style = "width: 70px;", numericInput("rep", label = NULL, value = 10, min = 1,))
)
```

### Costs

```{r}
selectInput(
  inputId = "y_axis",
  label = "Y-axis of costs plot",
  choices = c(
    "Cases at detection" = "cases",
    "Emergency department presentations at detection" = "hosp",
    "Time until detection" = "time"
    ),
  multiple = FALSE
)
```

Simulations
=======================================================================

### The blue dot shows the median number of days and number of infections upon detection by MBN, and error bars show the interquartile range. The grey lines show individual simulation runs.
```{r}
# set figure height
simulated_data <- eventReactive(input$run, {
  # Calculate average rate for the selected hospitals
  run_SEIR(
    disease_name = input$Disease_Scenario[[1]],
    rep = input$rep,
    threshold = input$Threshold,
    mu = coverage(input$selected_hospitals)
  )
})

observeEvent(input$select_top_n, {
  # Check if the input is within the available range
  if (input$top_n >= 1 && input$top_n <= length(Hospital_visitors$Hospital)) {
    # Select the top N hospitals
    top_n_hospitals <- head(Hospital_visitors$Hospital, n = input$top_n)
    updateSelectizeInput(session, "selected_hospitals", selected = top_n_hospitals)
  }
})

renderPlot({
  data <- simulated_data()
  plot_SEIR(data)
})
```

Cost-effectiveness
=======================================================================

### The blue line is the median outcome of 1000 pre-run simulations, and the grey area shows the interquartile range. In the sidebar, you can select a metric to show on the y-axis.
```{r}
subset_data <- reactive({
  results %>% 
    filter(d == input$Disease_Scenario, t == input$Threshold, output == input$y_axis)
})

renderPlot({plot_cost(subset_data())})
```

Model Documentation
=======================================================================

Row
-----------------------------------------------------------------------
```{r test, child="Documentation.RMD", eval=TRUE, local=TRUE}
```
